Forschungsprojekt

### 2020-10-14 documentation/presentation/main.tex
hugepages und conclusion

\section{Galois With Hugepages}
\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}

		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		& orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5\\
		& wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1\\
		& twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1\\
		& rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4\\
		& friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5\\
		& rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1\\
\end{tabular}
\includegraphics[width=8cm]{../../plots/singleNodeSSSPGaloisThreads.png}
\includegraphics[width=8cm]{../../plots/singleNodeSSSPGaloisHPThreads.png}

\section{Galois With Hugepages}
\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
	\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR Pull}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		& orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6\\
		& wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4\\
		& twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3\\
		& rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1\\
		& friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1\\
		& rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4\\
\end{tabular}
\includegraphics[width=0.5\linewidth]{../../plots/singleNodePRPullGaloisThreads.png}
\includegraphics[width=0.5\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}

\section{Conclusion and Outlook}
\begin{itemize}
	\item performance highly dependent on the framework, algorithm and data set
	\begin{itemize}
		\item Galois is almost always fastest in the research case; especially with hugepages
		\item Giraph is good on SSSP or BFS in distributed production
		\item Gemini is a good middleground for distributed PR and single node production
	\end{itemize}

	\item single node almost always preferrable, as long as RAM is sufficient
\end{itemize}

\subsection{Outlook}
\begin{itemize}
	\item[$\rightarrow$] incorporate new frameworks and new algorithms
	\item[$\rightarrow$] great range of settings and multiple implementations for the same problem
	\item[$\rightarrow$] At a later point in time, it is important to repeat such a comparison, because the frameworks are further developed and new ones are created.
\end{itemize}

>>>>

\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=1cm, right=1cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Galois With Hugepages on SSSP}
\begin{figure}[h!]
\hfil
\begin{subfigure}{0.33\linewidth}
	\sffamily
	\small
	\centering
	\begin{tabular}{cr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}
		&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{2-3}\cmidrule{4-5}
		\bf Graph&w/o&w/&w/o&w/\\
		\midrule
		flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5\\
		wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1\\
		twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1\\
		rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4\\
		friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5\\
		rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1\\
\end{tabular}
\end{subfigure}
\hfil
\begin{subfigure}{0.3\linewidth}
\centering
\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisThreads.png}
	\caption{Without Hugepages}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}
\centering
\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
	\caption{With Hugepages}
\end{subfigure}
\end{figure}
\begin{itemize}
	\item Hugepages further reduce both calculation and execution time
	\item Speedups with hugepages are \enquote{more reliable}, i.e., more predictable
\end{itemize}

\section{Galois With Hugepages on PR Pull}
\begin{figure}[h!]
\hfil
\begin{subfigure}{0.33\linewidth}
	\sffamily
	\small
	\centering
	\begin{tabular}{cr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
		&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{2-3}\cmidrule{4-5}
		\bf Graph&w/o&w/&w/o&w/\\
		\midrule
		flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6\\
		wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4\\
		twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3\\
		rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1\\
		friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1\\
		rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4\\
\end{tabular}
\end{subfigure}
\hfil
	\begin{subfigure}{0.3\linewidth}
	\centering
\includegraphics[width=\linewidth]{../../plots/singleNodePRPullGaloisThreads.png}
		\caption{Without Hugepages}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}
	\centering
\includegraphics[width=\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
		\caption{With Hugepages}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Hugepages further reduce both calculation and execution time
	\item Hugepages make speedup in multithreaded scenario possible
	\item Speedup not to the same degree as with SSSP (15$\times$ vs. 2.5$\times$)
\end{itemize}

\restoregeometry

\section{Conclusion and Outlook}
Generally: 1) performance highly dependent on the framework, algorithm and data set

2) single node almost always preferrable, as long as RAM is sufficient
\begin{multicols}{2}
	\subsection{Production Case}
	\begin{itemize}
		\item Giraph is very fast on distributed systems (especially SSSP and BFS), with added benefit of Hadoop (fault-tolerance, automatic parallelization) 
		\item Gemini (surprisingly) and Ligra are good options for single node 
	\end{itemize}

	\columnbreak
	\subsection{Research Case}
	\begin{itemize}
		\item Galois is fastest in almost all cases; further improvements with hugepages possible
	\end{itemize}
\end{multicols}

\subsection{Outlook}
\begin{itemize}
	\item[$\rightarrow$] incorporate new frameworks and new algorithms
	\item[$\rightarrow$] explore range of settings and other implementations
	\item[$\rightarrow$] repeat similar tests in the future: frameworks are improved and new ones are introduced
\end{itemize}
